Assessing glymphatic transport velocities by adjoint methods

### 2018-10-17 tex/paper.tex
restruct

\subsection*{Mathematical Model}
In order to estimate the apparent diffusion coefficient involved in the contrast transportation shown 
in Figure~\ref{fig1} we assume that the process can be modeled by a diffusion equation and  
solve a PDE constrained optimization problem where
the contrast distribution, boundary conditions, and apparent
diffusion coefficient are solved for by optimizing with
respect to the observed contrast distribution. As such, enhanced transportation because of effects such as
dissipation would result in an apparent diffusion coefficient larger than that predicted by DTI.  
The objective function was defined as 
\begin{equation}
\min_{u,g} F = \quad \sum\limits_i\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)| \mathrm{d}\Omega + \frac{\alpha}{2} \int\limits_{0}\sp{T} || g ||_{L\sp{2}(\partial\Omega)} \mathrm{d}t + \frac{\beta}{2} \int\limits_{0}\sp{T} || \dot{g} ||_{L\sp{2}(\partial\Omega)}\mathrm{d}t 
\label{EQ::objf}
\end{equation}
subject to   
\begin{equation}
\begin{aligned}
\frac{\partial u}{\partial t} = \nabla \cdot  D_i \nabla u \qquad \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
u=g(t) \qquad \text{on} \qquad \partial\Omega  \times \left\lbrace 0 , T \right) 
\end{aligned}
\label{Eq::PDE}
\end{equation}
Here, $u$ is the contrast distribution, $D_i$ is the apparent diffusion 
coefficient, and $g$ is the boundary condition. Furthermore,  
the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient. We denote the Cerebral Spinal fluid (CSF) domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$. The apparent
diffusion constant is assumed constant within the CSF, grey and 
white matter but each region may have different constants.  
The $\alpha$ and $\beta$ parameters are regularization parameters 
and $u_{obs}$ are observations at certain time-points.

\section*{Implementation}
The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements. The linear problem was solved using GMRES, and the matrix was stored in the solver. 
The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy. The convergence criteria for the minimization was set so that $max \lbrace | \text{proj} \hspace*{0.2cm} x_i | , \quad i = 1, .., N \rbrace \leq gtol=1.0e-1$ where $x_i$ is the i-th component of the gradient. {\color{red} From scipy :The iteration will stop when $max\lbrace | \text{proj} \hspace*{0.2cm} g_i | , \quad i = 1, .., N \rbrace \leq gtol $  where $pg_i$ is the i-th component of the projected gradient.}

@@

The difference in the calibraiton constant $M_0$ between observation times were adjusted in \cite{eidevalnes}. Thus we can express the $T_1$ change due to contrast as 

@@

The estimation of the tracer concentration was precomputed and used the parameters obtained from the T1 map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904}. In the computation, the function $f(T_1)$ was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table. The lookup table was utilized with the baseline intensity increase to estimate $T_1\sp{c}$, and then the concentration was computed using Eq.\ref{EQ::contrast}.

In \cite{sykova2008diffusion}, it was shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient. Thus the computed diffusion coefficients will correspond to the apparent diffusion coefficient.

In the acquired data, the MPRAGE had a high signal to noise ratio and the T1 map had low signal in the CSF. This made it difficult to estimate the concentration in the CSF compartment. Thus an additional mesh without the CSF compartment was constructed, see Fig. \ref{Fig::Mesh}.

@@

\subsection{PDE constrained optimization algorithm}

\kam{
Noen detaljer her om element methode, optimerings algoritme, prekondisjonering
grid, osv. 
}

\subsection*{Manufactured Solution}
In order to verify our strategy and test the dependency of the
regularization paramters, we perform a test case with a
known solution.  
The manufactured observations was obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
\begin{equation}
g(t)_{\partial \Omega_1} = 0.3 +0.167t - 0.007t\sp{2} \qquad  0 \leq t \leq 24.
\label{EQ::DIRI}
\end{equation}
The timestep was $dt = 0.02$, and the diffusion coefficients were selected to be 
\begin{equation}
D_{\Omega_1} = 1000 \quad , \quad D_{\Omega_2} = 4.0 \quad , \quad D_{\Omega_3} = 8.0 
\end{equation}  
The magnitude order for $\quad D_{\Omega_2} $ and $\quad D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coeffieicents were not preserved. The diffusion coefficent in the csf was chosen given [cite Bryne and Kent]. The manufactured forward computation gave a total of 120 possible observation time points. These points will be denoted as $t_i$.

@@

@@

\begin{figure}
\centering
\includegraphics[scale=0.2]{boundary_control.png}  
\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$. The left panel shows the legend for the plot over time, together with the selection of points. The middel panel shows the average bounadry value $g$ for different regularization parameter with $k=10$. The right panel shows the average bounadry value $g$ for different regularization parameter with $k=40$. }
\label{boundarycontrol}
\end{figure}

@@

The estimation of tracer concentration proved difficult in the CSF compartment. Therefore the 2 domain mesh, shown in Fig.\ref{Fig::Mesh} was used in the computation. The boundary control was set to the external boundary of both domains, and the subscript in $D_w$ and $D_g$ denotes white and grey diffusion coefficients. Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $gtol=6.0e-1$. The number of timesteps were selceted to be $k=48$, which gives approximate $dt = 1 hour$.

The results are shown in Tab.\ref{Tab::Real-data}, 
and the observation together with resulting states are displayed in Fig.\ref{Fig::realdata}

@@

The median diffusion coefficient in the DTI was estimated to be $8.7e-4 \mathrm{mm\sp{2}/s}$ in white matter and $1.0e-3 \mathrm{mm\sp{2}/s}$ in grey matter. This corresponds to $1.85$ and $1.73$ in tortuosity, given that the self-diffusivity of water has been estimated to be around $3.0e-3\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.% This corresponds to 10.8 $\mathrm{mm\sp{2}/h}$ and  $\mathrm{mm\sp{2}/h}$. 
Then by using the reference value $3.8e-4 \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the diffusion coefficient in the grey and white matter to respecitvly be $ 1.26\mathrm{mm\sp{2}/s}$ adn $1.10 \mathrm{mm\sp{2}/s}$. This estiamtion assums that the tortuoisty is indepedent on molecular size ? .

The oscillation in Fig.\ref{boundarycontrol} showed a large discrepency in the states between observations. Therefore the states after 36 hours were examined, see Figure  ~\ref{statecomparison}, and the upper rows some indications of non- optimal regularization parameters. This prompt the exclusion of the corresponding valeus, which gives an average computed values $0.65 \mathrm{mm\sp{2}/h}$ and  $0.80 \mathrm{mm\sp{2}/h}$ in respectively grey and white matter. Scaled to $\mathrm{mm\sp{2}/s}$ gives $1.8 \mathrm{mm\sp{2}/s}$ and $2.22 \mathrm{mm\sp{2}/s}$.

This gives a relative errot of $42 \%$ in grey matter and $ 100 %$ in white matter comparied the estimted values.

The computation require that there is tracer present to compute the diffusion coefficient. In Fig.\ref{Fig::realdata}, it can be seen that there are regions with neglible amount of tracers and vice versa. Considering $1.3 \mathrm{mm\sp{2}/s}$ as the upper boound gives an estimated upper bound $1.43$ diffusion coefficient in the white matter. This relative error of $54%$ difference.

@@

\section{Discussion}

%The results from the manufactured solutions showed a robust method to compute diffusion coefficients. However, the maufactured solutions were constructed .. ? .. .
The computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{figuredti}. The region with high FA, can also be observed in the observation after 48 hours, shown in Fig.\ref{Fig::realdata}. This observation is after 48 hours, and the amount of tracer inside the anisotropic region is negligible. Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment. Thus observation of tracer in anisotropic regions are needed for the integration of anisotropy into the model.

A more important factor are regions with higher diffusivity. Comparing Fig.\ref{figuredti} and Fig \ref{Fig::realdata}, it can be observed that the region with high diffusivity also have a high tracer concentration.

The computational model have 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{figuredti} that diffusion coefficients can be considered a spacial function. Although the implmentaion of spacial control parameters are possible, it would siginificantly increase the computational cost.

The coputational cost dependes on the relaxation parameteres, the number of controls and solution of the PDE.

It can also be taken into consideration to model the diffusion coefficients as a function in time, given the report of an increase clearance in rodents during sleeping [insert citation]. This follows the assumption that the clearance is related to diffusion, which means an increase in diffusivity. Since the properties of the tracer molecule do not change, this would mean that the tortuosity decreased and followed by an incearse in the ADC.

In Tab.\ref{Tab::Real-data}, it is shown that the grey matter diffusion coefficient have a consistent increase based on the decrease in the relaxation parameter $\beta$. This can be caused by the boundary control $g$, which exists along the entire boundary of the grey matter. Considering the that the grey matter volume has a depth less than 3 mm makes it susceptible to changes in $g$. This can be observed in the reconstruction in Fig.\ref{12hourswithnoise} and Fig.\ref{24hourswithnoise}, where the nosie is present at the boundary.

A possible solution is to include the CSF compartment, but only use the observation in the white and grey matter.

@@

%\begin{figure}
%\centering
%\includegraphics[scale=0.4]{27-12-hours-scale-0-1-3.png}  
%\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15. C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$. D) Shows the resulting state given the observation in A. E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C. }
%\end{figure}
%
%
%\begin{figure}
%\centering
%\includegraphics[scale=0.4]{27-24-hours-scale-0-1.png}
%\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15 {\color{red} explain noise ampliutde}. C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$. D) Shows the resulting state given the observation in A. E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.  }
%\end{figure}
% 
% 
% 
%
%

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{different.png} 
\caption{Row A) shows the observation at times 2 hours, 6 hours, 24 hours and 48 hours after the first observation with tracer. Row B) shows the corresponding states with the relaxation parameters set to $ \alpha=0.01$ and $\beta=0.01$.   Row C) shows the corresponding states with the relaxation parameters set to $ \alpha=0.0001$ and $\beta=1.0$.
 Row D) shows the corresponding states with the relaxation parameters set to$ \alpha=1.0e-6$ and $\beta=0.1$. The color-bar was restricted to the range $ \lbrace 0 ,0.5 \rbrace$. }
\label{Fig::realdata}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{Statecomparison36h-pinta.png} 
\caption{ Displays the states for different regularixation parameters after 36 h.}
\label{statecomparison}
\end{figure}

@@

\begin{table}
\centering
\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$. }
\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $&$|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $ \\
\hline
 %1.0e+00 	 & 1.0e+00 	 & 10 & 128 	 & +1.587 & +0.217 & +0.091 & +0.119 \\ 
 1.0e+00 	 & 1.0e+00 	 & 20 & 268 	 & +5.537 & +0.321 & +0.152 & +0.128 \\ 
 1.0e+00 	 & 1.0e+00 	 & 40 & 381 	 & +12.346 & +0.890 & +0.249 & +0.154\\

@@

% 1.0e-04 	 & 1.0e+00 	 & 10 & 140 	 & -0.048 & +0.032 & +0.035 & +0.026 \\ 
 1.0e-04 	 & 1.0e+00 	 & 20 & 165 	 & +0.006 & +0.000 & +0.008 & +0.007 \\ 
 1.0e-04 	 & 1.0e+00 	 & 40 & 285 	 & +0.005 & -0.013 & +0.000 & +0.003 \\ 
 1.0e-04 	 & 1.0e+00 	 & 20 & 187 	 & -0.007 & +0.004 & +0.013 & +0.008 \\ 
 1.0e-04 	 & 1.0e+00 	 & 40 & 257 	 & -0.019 & -0.019 & +0.005 & +0.007 \\ 
 %1.0e-04 	 & 1.0e-01 	 & 20 & 367 	 & +0.028 & +0.010 & +0.008 & +0.007 \\
 %1.0e-04 	 & 1.0e-01 	 & 40 & 422 	 & +0.001 & -0.007 & +0.004 & +0.005 \\  
 1.0e-04 	 & 1.0e-02 	 & 20 & 258 	 & +0.068 & +0.023 & +0.005 & +0.006 \\ 
 1.0e-04 	 & 1.0e-02 	 & 40 & 339 	 & +0.004 & +0.002 & +0.002 & +0.003 \\

@@

% 1.0e-05 	 & 1.0e+00 	 & 20 & 237 	 & -0.006 & +0.004 & +0.013 & +0.008 \\ 
 %1.0e-05 	 & 1.0e+00 	 & 40 & 358 	 & -0.018 & -0.019 & +0.005 & +0.007 \\  
 %1.0e-05 	 & 1.0e-01 	 & 20 & 290 	 & +0.026 & +0.010 & +0.008 & +0.007 \\
 %1.0e-05 	 & 1.0e-01 	 & 40 & 419 	 & +0.001 & -0.007 & +0.004 & +0.005 \\    
 %1.0e-05 	 & 1.0e-02 	 & 20 & 316 	 & +0.071 & +0.025 & +0.005 & +0.007 \\ 
 %1.0e-05 	 & 1.0e-02 	 & 40 & 401 	 & +0.004 & +0.003 & +0.002 & +0.004 \\  
 1.0e-06 	 & 1.0e+00 	 & 20 & 219 	 & -0.007 & +0.004 & +0.013 & +0.008 \\ 
 1.0e-06 	 & 1.0e+00 	 & 40 & 240 	 & -0.020 & -0.019 & +0.005 & +0.007 \\ 
 %1.0e-06 	 & 1.0e-01 	 & 20 & 250 	 & +0.027 & +0.010 & +0.008 & +0.007 \\ 
 %1.0e-06 	 & 1.0e-01 	 & 40 & 365 	 & +0.000 & -0.007 & +0.004 & +0.005 \\ 
 1.0e-06 	 & 1.0e-02 	 & 20 & 379 	 & +0.070 & +0.025 & +0.005 & +0.007 \\ 
 1.0e-06 	 & 1.0e-02 	 & 40 & 386 	 & +0.004 & +0.003 & +0.002 & +0.004 \\ 
\end{tabular}
\label{TAB::timesteps}
\end{table}

>>>>

@@

The intensity difference between observation times were adjusted in \cite{eidevalnes}. Thus we can express the $T_1$ change due to contrast as 

@@

@@

\subsection*{Mathematical Model}

In \cite{sykova2008diffusion}, It was shown that the macroscopic diffusion in the brain can be considered a hindered diffusion with an apparent diffusion coefficient.

In order to estimate the apparent diffusion coefficient involved in the contrast transportation shown in Figure~\ref{fig1} we assume that the process can be modeled by a diffusion equation and solve a PDE constrained optimization problem where
the contrast distribution, boundary conditions, and apparent
diffusion coefficient are solved for by optimizing with
respect to the observed contrast distribution. As such, enhanced transportation because of effects such as
dissipation would result in an apparent diffusion coefficient larger than that predicted by DTI.  
The objective function was defined as 
\begin{equation}
\min_{u,g} F = \quad \sum\limits_i\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)| \mathrm{d}\Omega + \frac{\alpha}{2} \int\limits_{0}\sp{T} || g ||_{L\sp{2}(\partial\Omega)} \mathrm{d}t + \frac{\beta}{2} \int\limits_{0}\sp{T} || \dot{g} ||_{L\sp{2}(\partial\Omega)}\mathrm{d}t 
\label{EQ::objf}
\end{equation}
subject to   
\begin{equation}
\begin{aligned}
\frac{\partial u}{\partial t} = \nabla \cdot  D_i \nabla u \qquad \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
u=g(t) \qquad \text{on} \qquad \partial\Omega  \times \left\lbrace 0 , T \right) 
\end{aligned}
\label{Eq::PDE}
\end{equation}
Here, $u$ is the contrast distribution, $D_i$ is the apparent diffusion 
coefficient, and $g$ is the boundary condition. Furthermore,  
the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient. We denote the Cerebral Spinal fluid (CSF) domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$. The apparent
diffusion constant is assumed constant within the CSF, grey and 
white matter but each region may have different constants.  
The $\alpha$ and $\beta$ parameters are regularization parameters 
and $u_{obs}$ are observations at certain time-points.

\subsection*{Manufactured Solution}
In order to verify our strategy and test the dependency of the
regularization paramters, we perform a test case with a
known solution.  
The manufactured observations was obtained by forward computation of Eq.\ref{Eq::PDE} with the Dirichlet boundary condition defined as
\begin{equation}
g(t)_{\partial \Omega_1} = 0.3 +0.167t - 0.007t\sp{2} \qquad  0 \leq t \leq 24.
\label{EQ::DIRI}
\end{equation}
The timestep was $dt = 0.02$, and the diffusion coefficients were selected to be 
\begin{equation}
D_{\Omega_1} = 1000 \quad , \quad D_{\Omega_2} = 4.0 \quad , \quad D_{\Omega_3} = 8.0 
\end{equation}  
The magnitude order for $\quad D_{\Omega_2} $ and $\quad D_{\Omega_2}$ were chosen to resemble diffusion coefficient for water in grey and white matter, but the relation between the coefficients were not preserved. The diffusion coefficient in the CSF was chosen given [cite Bryne and Kent], and the initial condition was set to 1.0 in $\Omega_1$ and 0 elsewhere. The manufactured forward computation gave a total of 120 possible observation time points. These points will be denoted as $t_i$.

@@

\section*{Implementation}
The estimation of the tracer concentration was precomputed and used the parameters obtained from the T1 map, MPRAGE MRI protocol \cite{eidevalnes} and the value for $r_1$ found in \cite{pmid16230904}. In the computation, the function $f(T_1)$ was computed for $ T_1\in \lbrace 200, 4000 \rbrace$ creating a lookup table. The lookup table was utilized with the baseline intensity increase to estimate $T_1\sp{c}$, and then the concentration was computed using Eq.\ref{EQ::contrast}.

%In the acquired data, the MPRAGE had a high signal to noise ratio and the T1 map had low signal in the CSF. This made it difficult to estimate the concentration in the CSF compartment. Thus an additional mesh without the CSF compartment was constructed, see Fig. \ref{Fig::Mesh}.

The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements. The linear problem was solved using GMRES, and the matrix was stored in the solver. 
The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm in the python module scipy. The convergence criteria for the minimization was set so that $max \lbrace | \text{proj} \hspace*{0.2cm} x_i | , \quad i = 1, .., N \rbrace \leq gtol=1.0e-1$ where $x_i$ is the i-th component of the gradient. {\color{red} From scipy :The iteration will stop when $max\lbrace | \text{proj} \hspace*{0.2cm} g_i | , \quad i = 1, .., N \rbrace \leq gtol $  where $pg_i$ is the i-th component of the projected gradient.}

@@

\begin{figure}
\centering
\includegraphics[scale=0.2]{boundary_control.png}  
\caption{ Displays plots over time for a selection of points at the boundary of $\Omega_1$ with different regularization parameters and number of timesteps $k$. The left panel shows the legend for the plot over time, together with the selection of points. The middle panel shows the average boundary value $g$ for different regularization parameter with $k=10$. The right panel shows the average boundary value $g$ for different regularization parameter with $k=40$. }
\label{boundarycontrol}
\end{figure}

@@

The estimation of tracer concentration proved difficult in the CSF compartment. Therefore the 2 domain mesh, shown in Fig.\ref{Fig::Mesh} was used in the computation. The boundary control was set to the external boundary of both domains, and the subscript in $D_w$ and $D_g$ denotes white and grey diffusion coefficients. Furthermore, bounds were added to the L-BFGS-B algorithm to ensure non-negative boundary controls and the convergence criteria was adjusted to $gtol=6.0e-1$. The number of timesteps were selected to be $k=24$ $k=48$, which gives $dt = 2 hour$ and $dt = 1 hour$.

The results are shown in Tab.\ref{Tab::Real-data}, and the observations after 12 and 48 hours were compared with the corresponding states.

@@

The median diffusion coefficient in the DTI was estimated to be $8.7e-4 \mathrm{mm\sp{2}/s}$ in white matter and $1.0e-3 \mathrm{mm\sp{2}/s}$ in grey matter. This corresponds to $1.85$ and $1.73$ in tortuosity, given that the self-diffusivity of water has been estimated to be around $3.0e-3\mathrm{mm\sp{2}/s}$ at $37\sp{o}C$.% This corresponds to 10.8 $\mathrm{mm\sp{2}/h}$ and  $\mathrm{mm\sp{2}/h}$. 
Then by using the reference value $3.8e-4 \mathrm{mm\sp{2}/s}$ for Gd-DPTA gives an estimate for the diffusion coefficient in the grey and white matter to respectively be $ 1.26\mathrm{mm\sp{2}/s}$ and $1.10 \mathrm{mm\sp{2}/s}$. This estimation assumes that the tortuosity is independent on molecular size .

The oscillation in Fig.\ref{boundarycontrol} showed a large discrepancy in the states between observations. Therefore the states with $k=48$ were examined after 36 hours, see Figure\ref{statecomparison}. It can be observed that the upper right row displays a discrepancy, which likely due to wrong regularization parameters. This prompt the exclusion of the corresponding values, which gives an average computed values $0.65 \mathrm{mm\sp{2}/h}$ and  $0.80 \mathrm{mm\sp{2}/h}$ in respectively grey and white matter. Scaled to $\mathrm{mm\sp{2}/s}$ gives $1.8 \mathrm{mm\sp{2}/s}$ and $2.22 \mathrm{mm\sp{2}/s}$.

This gives a relative error of $42 \%$ in grey matter and $ 100 \%$ in white matter compared to the estimated values.

The computation require that there is tracer present to compute the diffusion coefficient. In Fig.\ref{Fig::realdata}, it can be seen that there are regions with negligible amount of tracers and vice versa. Considering $1.3 \mathrm{mm\sp{2}/s}$ as the upper bound gives an estimated upper bound $1.43$ diffusion coefficient in the white matter. This relative error of $54\%$ difference {\color{red} compare with dispersion, NB bare k 48 er brukt, k 24 skal med}

@@

\section{Discussion}
The computational model assumes isotropic diffusivity, but the anisotropy in the white matter is well documented, as shown by the FA in Fig\ref{figuredti}. Furthermore, it can be seen in Figure~\ref{Fig::realdata} that the region with high FA have negligible amounts of tracer present. Therefore it would seem that the anisotropy do not have direct impact on the computations, since the computation can not evaluate a static environment. Therefore  observation of tracer in regions with anisotropy can be considered a requirement for adding anisotropy to the model.

The regions with high diffusivity in Figure~\ref{figuredti},  have significant amount of diffusivity as seen in Figure~\ref{Fig::realdata}

The computational model have 2 global controls for the diffusion coefficients, while it can be seen in  Fig.\ref{figuredti} that diffusion coefficients can be considered a spacial function. Although the implementation of spacial control parameters are possible, it would significantly increase the computational cost.

It can also be taken into consideration to model the diffusion coefficients as a function in time, given the report of an increase clearance in rodents during sleeping [insert citation]. This follows the assumption that the clearance is related to diffusion, which means an increase in diffusivity. Since the properties of the tracer molecule do not change, this would mean that the tortuosity decreased and followed by an increase in the ADC.

In Tab.\ref{Tab::Real-data}, it is shown that the grey matter diffusion coefficient have a consistent increase based on the decrease in the relaxation parameter $\beta$. This can be caused by the boundary control $g$, which exists along the entire boundary of the grey matter. Considering the that the grey matter volume has a depth less than 3 mm makes it susceptible to changes in $g$. This can be observed in the reconstruction in Fig.\ref{12hourswithnoise} and Fig.\ref{24hourswithnoise}, where the noise is present at the boundary.

@@

%\begin{figure}
%\centering
%\includegraphics[scale=0.4]{27-12-hours-scale-0-1-3.png}  
%\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15. C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$. D) Shows the resulting state given the observation in A. E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C. }
%\end{figure}
%
%
%\begin{figure}
%\centering
%\includegraphics[scale=0.4]{27-24-hours-scale-0-1.png}
%\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15 {\color{red} explain noise ampliutde}. C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$. D) Shows the resulting state given the observation in A. E)  Shows the resulting state given the observation in B .F) Shows the resulting state given the observation in C.  }
%\end{figure}
% 
% 
% 
%
% 
\section{References}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{different.png} 
\caption{Row A) shows the observation at times 2 hours, 6 hours, 24 hours and 48 hours after the first observation with tracer. Row B) shows the corresponding states with the relaxation parameters $\alpha=0.01$ and $\beta=0.01$ and $k=48$.   Row C) shows the corresponding states with the relaxation parameters $\alpha=0.0001$ and $\beta=1.0$ and $k=48$
 Row D) shows the corresponding states with the relaxation parameters $\alpha=1.0e-6$ and $\beta=0.1$ and $k=48$. The color-bar was restricted to the range $ \lbrace 0 ,0.5 \rbrace$. }
\label{Fig::realdata}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{Statecomparison36h-pinta.png} 
\caption{ Displays the states for different regularization parameters after 36 hours for $k=48$.}
\label{statecomparison}
\end{figure}

@@

\begin{table}
\centering
\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$. }
\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $&$|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $ \\
\hline

 %1.0e+00 	 & 1.0e+00 	 & 10 & 128 	 & +1.587 & +0.217 & +0.091 & +0.119 \\

 1.0e+00 	 & 1.0e+00 	 & 20 & 268 	 & +5.537 & +0.321 & +0.152 & +0.128 \\ 
 1.0e+00 	 & 1.0e+00 	 & 40 & 381 	 & +12.346 & +0.890 & +0.249 & +0.154\\

 1.0e+00 	 & 1.0e-02 	 & 20 & 407 	 & +17.676 & +1.417 & +0.402 & +0.251 \\ 
 1.0e+00 	 & 1.0e-02 	 & 40 & 873 	 & +61.467 & +17.965 & +16.437 & +0.614 \\

@@

 1.0e-02 	 & 1.0e+00 	 & 20 & 157 	 & +0.016 & +0.004 & +0.008 & +0.007 \\ 
 1.0e-02 	 & 1.0e+00 	 & 40 & 277 	 & +0.020 & -0.006 & +0.001 & +0.003 \\

 1.0e-02 	 & 1.0e-02 	 & 20 & 447 	 & +0.130 & +0.055 & -0.000 & +0.016 \\ 
 1.0e-02 	 & 1.0e-02 	 & 40 & 458 	 & +0.098 & +0.088 & +0.002 & +0.023 \\

 1.0e-02 	 & 1.0e-04 	 & 20 & 595 	 & +0.175 & +0.081 & -0.003 & +0.090 \\ 
 1.0e-02 	 & 1.0e-04 	 & 40 & 976 	 & +0.320 & +0.398 & +0.088 & +0.226 \\

% 1.0e-04 	 & 1.0e+00 	 & 10 & 140 	 & -0.048 & +0.032 & +0.035 & +0.026 \\ 
 1.0e-04 	 & 1.0e+00 	 & 20 & 165 	 & +0.006 & +0.000 & +0.008 & +0.007 \\ 
 1.0e-04 	 & 1.0e+00 	 & 40 & 285 	 & +0.005 & -0.013 & +0.000 & +0.003 \\ 
 %1.0e-04 	 & 1.0e-01 	 & 20 & 367 	 & +0.028 & +0.010 & +0.008 & +0.007 \\
 %1.0e-04 	 & 1.0e-01 	 & 40 & 422 	 & +0.001 & -0.007 & +0.004 & +0.005 \\  
 1.0e-04 	 & 1.0e-02 	 & 20 & 258 	 & +0.068 & +0.023 & +0.005 & +0.006 \\ 
 1.0e-04 	 & 1.0e-02 	 & 40 & 339 	 & +0.004 & +0.002 & +0.002 & +0.003 \\

@@

% 1.0e-05 	 & 1.0e+00 	 & 20 & 237 	 & -0.006 & +0.004 & +0.013 & +0.008 \\ 
 %1.0e-05 	 & 1.0e+00 	 & 40 & 358 	 & -0.018 & -0.019 & +0.005 & +0.007 \\  
 %1.0e-05 	 & 1.0e-01 	 & 20 & 290 	 & +0.026 & +0.010 & +0.008 & +0.007 \\
 %1.0e-05 	 & 1.0e-01 	 & 40 & 419 	 & +0.001 & -0.007 & +0.004 & +0.005 \\    
 %1.0e-05 	 & 1.0e-02 	 & 20 & 316 	 & +0.071 & +0.025 & +0.005 & +0.007 \\ 
 %1.0e-05 	 & 1.0e-02 	 & 40 & 401 	 & +0.004 & +0.003 & +0.002 & +0.004 \\  
 1.0e-06 	 & 1.0e+00 	 & 20 & 219 	 & -0.007 & +0.004 & +0.013 & +0.008 \\ 
 1.0e-06 	 & 1.0e+00 	 & 40 & 240 	 & -0.020 & -0.019 & +0.005 & +0.007 \\ 
 %1.0e-06 	 & 1.0e-01 	 & 20 & 250 	 & +0.027 & +0.010 & +0.008 & +0.007 \\ 
 %1.0e-06 	 & 1.0e-01 	 & 40 & 365 	 & +0.000 & -0.007 & +0.004 & +0.005 \\ 
 1.0e-06 	 & 1.0e-02 	 & 20 & 379 	 & +0.070 & +0.025 & +0.005 & +0.007 \\ 
 1.0e-06 	 & 1.0e-02 	 & 40 & 386 	 & +0.004 & +0.003 & +0.002 & +0.004 \\

 1.0e-06 	 & 1.0e-04 	 & 20 & 356 	 & +0.101 & +0.028 & -0.002 & +0.021 \\ 
 1.0e-06 	 & 1.0e-04 	 & 40 & 410 	 & -0.011 & -0.002 & -0.003 & +0.004 \\ 
\end{tabular}
\label{TAB::timesteps}
\end{table}

\begin{table}
\centering
\caption{ Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated diffusion coefficients and the relative error for $g$. The observation times were set $t_i \in \lbrace 4.8, 9.6, 14.4, 19.2, 24.0 \rbrace $. }
\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1}\sp{rel}$& $D_{\Omega_2}\sp{rel} $ & $D_{\Omega_3}\sp{rel} $&$|| g ||\sp{rel}_{L\sp{2}(\Omega_1)} $ \\
\hline

 %1.0e-04 	 & 1.0e+02 	 & 10 & 895 	 & +22.689 & +0.254 & +0.008 & +0.024 \\ 
 %1.0e-04 	 & 1.0e+02 	 & 20 & 1001 	 & +13.781 & +0.142 & -0.026 & +0.025 \\
 %1.0e-04 	 & 1.0e+02 	 & 40 & 1001 	 & +9.368 & +0.089 & -0.042 & +0.026 \\

% 1.0e-06 	 & 1.0e+02 	 & 10 & 919 	 & +19.507 & +0.255 & +0.008 & +0.024 \\ 
% 1.0e-06 	 & 1.0e+02 	 & 20 & 999 	 & +15.032 & +0.141 & -0.026 & +0.025 \\ 
% 1.0e-06 	 & 1.0e+02 	 & 40 & 1001 	 & +9.809 & +0.088 & -0.043 & +0.026 \\
